A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-07-09 tex/sec5-synthesis.tex
[ tex ] Trichotomy in the end of S5

\section{Bidirectional Type Synthesis and Checking} \label{sec:type-synthesis}
This section focuses on defining mode-correctness and deriving bidirectional type synthesis for any mode-correct bidirectional type system $(\Sigma, \Omega)$.
\LT{trichotomy first or last?}
We start with the statement of the decidability of bidirectional synthesis and the trichotomy on raw terms for mode-correct bidirectional type systems in \Cref{subsec:trichotomy}, but defer the definition of mode-correctness until \Cref{sec:mode-correctness} and the decidability proof until \Cref{subsec:bidirectional-synthesis-checking}.
We will then formalise mode-correctness and show the uniqueness of synthesized types in \Cref{sec:mode-correctness}.
This uniqueness property means that any two synthesised types for the same raw term $t$ under the same context $\Gamma$ have to be equal.
This will be used later in the proof of the decidability of bidirectional type synthesis and checking in \Cref{subsec:bidirectional-synthesis-checking}.

>>>>

\section{Bidirectional Type Synthesis and Checking} \label{sec:type-synthesis}
This section focuses on defining mode-correctness and deriving bidirectional type synthesis for any mode-correct bidirectional type system $(\Sigma, \Omega)$.
We start with \Cref{sec:mode-correctness} by defining mode-correctness and showing the uniqueness of synthesized types.
This uniqueness means that any two synthesised types for the same raw term $t$ under the same context $\Gamma$ have to be equal.
It will be used especially in \Cref{subsec:bidirectional-synthesis-checking} for the proof of the decidability of bidirectional type synthesis and checking.
Then, we conclude this section with the trichotomy on raw terms that has been illustrated at the beginning in \Cref{subsec:trichotomy}.
